---
title: "CBMC-Fish Price Monitoring"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: sandstone
runtime: shiny
resource_files:
- .secrets/bb8565617b5e9996ff93e6d214ba7218_favoretto@uabcs.mx
---

```{r setup, include=FALSE}

library(shiny)
library(flexdashboard)
library(tidyverse)
library(patchwork)
library(plotly)
library(see)

sniim <- data.table::fread("https://www.dropbox.com/s/e9altoa7v8zxzvg/ts_summary.csv?dl=1")

results <- data.table::fread("https://www.dropbox.com/s/c7xe1g05643re32/last_prices.csv?dl=1")

```

Price Selector
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

Select a species name below to see the price stats.  
```{r}

selectInput("species3", label = "Species:",
            choices = sniim %>% 
                      select(product_short_name) %>% 
                      unique() %>% 
                      pull() %>% 
                      sort(.), 
            selected = "Huachinango")


```

Row
-----------------------------------------------------------------------

### `r paste0("Last average price [updated ", print(results %>% pull(date) %>% max(., na.rm = T)), "]")` {.value-box}

```{r}

renderValueBox({
  ratef <- formatC( 
    results %>%
    filter(product_short_name == as.character(input$species3)) %>% 
    filter(date == max(date, na.rm = T)) %>% 
      ungroup() %>% 
    summarise(p_mean = mean(price_mxn, na.rm = T)) %>%  
      pull(p_mean), 
    digits = 1, format = "f")
  rate <- results %>%
    filter(product_short_name == as.character(input$species3)) %>% 
    filter(date == max(date, na.rm = T)) %>% 
      ungroup() %>% 
    summarise(p_mean = mean(price_mxn, na.rm = T)) %>%  
      pull(p_mean) %>% 
            round(.,1)
  hist <- sniim %>%
    filter(product_short_name == as.character(input$species3)) %>% 
      ungroup() %>% 
    summarise(p_mean = mean(price_mxn, na.rm = T)) %>%  
      pull(p_mean)%>% 
            round(.,1)
  
  valueBox(
    value = ratef,
    icon = ifelse(rate == hist, "fa-equals", ifelse(rate > hist, "fa-angle-up", "fa-angle-down")), 
    color = ifelse(rate > hist, "danger", "info")
  )
})

```

### Historical average {.value-box}

```{r}

renderValueBox({
  rate <- formatC( 
    sniim %>%
    filter(product_short_name == as.character(input$species3)) %>% 
      ungroup() %>% 
    summarise(p_mean = mean(price_mxn, na.rm = T)) %>%  
      pull(p_mean), 
    digits = 1, format = "f")
  valueBox(
    value = rate
  )
})
```

### `r renderText({paste0("Minimum day price reported in: ", print(results %>%  filter(product_short_name == as.character(input$species3)) %>% filter(date == max(date, na.rm = T)) %>% filter(price_mxn == min(price_mxn, na.rm=T)) %>% pull(origin_name) %>%  unique()))})` {.value-box}

```{r}

renderValueBox({
  
   rate <- formatC( 
    results %>%
    filter(product_short_name == as.character(input$species3)) %>% 
    filter(date == max(date, na.rm = T)) %>% 
    filter(price_mxn == min(price_mxn, na.rm = T)) %>% 
    ungroup() %>%
    pull(price_mxn) %>% 
    unique(), 
    digits = 1, format = "f")
   
  valueBox(
    value = rate
  )
})
```

### `r renderText({paste0("Maximum day price reported in: ", print(results %>%  filter(product_short_name == as.character(input$species3)) %>% filter(date == max(date, na.rm = T)) %>% filter(price_mxn == max(price_mxn, na.rm = T)) %>%  pull(origin_name) %>%  unique()))})` {.value-box}

```{r}

renderValueBox({
   
   rate <- formatC( 
    results %>%
    filter(product_short_name == as.character(input$species3)) %>% 
    filter(date == max(date, na.rm = T)) %>% 
    filter(price_mxn == max(price_mxn, na.rm = T)) %>%   
    ungroup() %>%
    pull(price_mxn) %>% 
    unique(), 
    digits = 1, format = "f")
   
  valueBox(
    value = rate
  )
})
```




Time trends 
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

Select a species name below to see the price trends. 

```{r}

selectInput("species4", label = "Species:",
            choices = sniim %>% 
                      select(product_short_name) %>% 
                      unique() %>% 
                      pull() %>% 
                      sort(.), 
            selected = "Huachinango")


```

Row
-----------------------------------------------------------------------


### Historical trend

```{r}
renderPlotly({
  
sniim %>%
          filter(product_short_name == as.character(input$species4)) %>% 
          ggplot(aes(x = date, y = price_mxn)) +
          #geom_point(col = "white") +
          #geom_line(col = "white") +
          geom_smooth(col = "white") +
          labs(x="Year", y="Price in MXN pesos") +
          theme_abyss()
})


```

Row
-----------------------------------------------------------------------

### Seasonal trend

```{r}
renderPlotly({
  sniim %>%
          filter(product_short_name == as.character(input$species4)) %>% 
          mutate(month = lubridate::month(date)) %>% 
          group_by(month, product_short_name) %>% 
          summarise(price_mxn = mean(price_mxn)) %>% 
          ggplot(aes(x = month, y = price_mxn)) +
          geom_line(col = "white") +
          labs(x="Month", y="Price in MXN pesos") +
          scale_x_continuous(breaks = seq(1,12, by=1)) +
          theme_abyss()

})


```

